A re-examination of the role of friction in the original Social Force Model

### 2019-06-23 paper.tex
modifique las comillas de las referencias

  \bibitem{Hirai}
Hirai, K., and Tarui, K., 1975. A simulation of the behavior of 
a crowd in panic, Proceedings of the 1975 International
Conference on Cybernetics Society, pp. 409-411

 \bibitem[Okazaki (1979)]{Okazaki}
Okazaki, S., 1979. A study of pedestrian movement in 
architectural space, Part 
1: pedestrian movement by the application of magnetic model. Trans. A.I.J. 283, 
111–119.

\bibitem{Helbing1}
Helbing, D., Farkas, I., and Vicsek, T., 2000. "Simulating dynamical 
features of escape panic." Nature 407.6803: 487-490. 
{\path{https://doi.org/10.1038/35035023}}

\bibitem{Helbing4}
Helbing, D., and Moln\'ar, P., 1995. "Social force model for pedestrian 
dynamics." Physical review E 51 (5), 4282. 
{\path{https://doi.org/10.1103/PhysRevE.51.4282}}

\bibitem{Dorso2}
Parisi, D. R., and Dorso, C. O., 2007. "Morphological and dynamical 
aspects of the room evacuation process." Physica A: Statistical Mechanics and 
its Applications 385 (1), 343-355. 
{\path{https://doi.org/10.1016/j.physa.2007.06.033}}

\bibitem{Dorso1}
Parisi, D. R., and Dorso, C. O., 2005. "Microscopic dynamics of pedestrian 
evacuation." Physica A: Statistical Mechanics and its Applications 354, 
606-618. {\path{https://doi.org/10.1016/j.physa.2005.02.040}}

\bibitem{Dorso3}
Frank, G. A., and Dorso, C. O., 2011. "Room evacuation in 
the presence of an obstacle." Physica A: Statistical Mechanics and its 
Applications 390 (11), 2135-2145. 
{\path{https://doi.org/10.1016/j.physa.2011.01.015}}

\bibitem{Dorso5}
Sticco, I. M., Frank, G. A., and Dorso, C. O., 2017. "Room evacuation 
through two contiguous exits." Physica A: Statistical Mechanics and its 
Applications 474, 172-185. 
{\path{https://doi.org/10.1016/j.physa.2017.01.079}}

\bibitem{Cornes1}
Cornes, F. E., Frank, G. A., and Dorso, C. O., 2017. "High pressures in room 
evacuation processes and a first approach to the dynamics around unconscious 
pedestrians." Physica A: Statistical Mechanics and its Applications 484, 
282-298. {\path{https://doi.org/10.1016/j.physa.2017.05.013}}

\bibitem{Dorso4}
Frank, G. A., and Dorso, C. O., 2015. "Evacuation under limited 
visibility." International Journal of Modern Physics C 26.01, 1550005.
{\path{https://doi.org/10.1142/S0129183115500059}}

\bibitem{Dorso6}
Frank, G. A., and Dorso, C. O., 2016. "Panic evacuation of single pedestrians 
and couples." International Journal of Modern Physics C 27.08, 1650091. 
{\path{https://doi.org/10.1142/S0129183116500911}}

\bibitem{koster1}
K\"oster, G., Treml, F. and G\"odel, M., 2013. "Avoiding 
numerical pitfalls in social force models." Physical Review E 87 (6), 063305.
{\path{https://doi.org/10.1103/PhysRevE.87.063305}}

\bibitem{chraibi1}
Seyfried, A., Schadschneider, A., Wagoum, K., Ulrich, A. and Mohcine, C., 
2011. "Force-based models of pedestrian dynamics." Networks 
\& Heterogeneous Media 6 (3), 425-442.
{\path{10.3934/nhm.2011.6.425}}

\bibitem{dietrich1}
Dietrich, F., K\"oster, G., Seitz, M. and 
von Sivers, I., 2014. "Bridging the gap: From cellular automata to 
differential equation models for pedestrian dynamics." Journal of Computational 
Science 5 (5), 841-846.{\path{https://doi.org/10.1016/j.jocs.2014.06.005}}

\bibitem{Lakoba}
Lakoba, T. I., Kaup, D. J., and Finkelstein, N. M., 2005. "Modifications of the 
Helbing-Molnar-Farkas-Vicsek social force model for pedestrian evolution." 
Simulation 81 (5), 339-352.
{\path{https://doi.org/10.1177/0037549705052772}}

\bibitem{Boltes}
Boltes, M., Zhang, J., Tordeux, A., Schadschneider A., Seyfried 
A., 
2018. Empirical Results of Pedestrian and Evacuation Dynamics. In: Meyers R. 
(eds) Encyclopedia of Complexity and Systems Science. Springer, Berlin, 
Heidelberg

\bibitem{helbing3}
Helbing, D., Johansson, A., and Al-Abideen, H. Z., 2007. "Dynamics of crowd 
disasters: An empirical study." Physical review E 75 (4), 046109.
{\path{https://doi.org/10.1103/PhysRevE.75.046109}}

@@

\bibitem{seyfried}
Seyfried, A., Boltes, M., K\"ahler, J., Klingsch, W., Portz, A., Rupprecht, 
T., Schadschneider, A., Steffen, B. and Winkens, A., 2010. "Enhanced empirical 
data for the fundamental diagram and the flow through bottlenecks." Pedestrian 
and Evacuation Dynamics 2008. Springer, Berlin, Heidelberg. 145-156.
{\path{https://doi.org/10.1007/978-3-642-04504-2\_11}}

\bibitem{lohner1}
L\"ohner, R., Muhamad, B., Dambalmath, P., and Haug, E., 2018. 
"Fundamental diagrams for specific very high density crowds." Collective 
Dynamics 2, 1-15.
{\path{http://dx.doi.org/10.17815/CD.2017.13}}

\bibitem{Dridi1}
Dridi, M. (2015) Pedestrian Flow Simulation Validation and
Verification Techniques. Current Urban Studies, 3, 119-134.
doi: 10.4236/cus.2015.32011.

\bibitem{Dridi2}
Dridi, M. (2015) Simulation of High Density Pedestrian Flow:
A Microscopic Model. Open Journal of Modelling and Simulation,
3, 81-95. doi: 10.4236/ojmsi.2015.33009.

\bibitem{Baqui1}
Baqui, M., and L\"ohner, R. "Real-time crowd safety
and comfort management from CCTV images." Real-Time Image and Video Processing 2017.
Vol. 10223. International Society for Optics and Photonics, 2017.

\bibitem{lohner2}
L\"ohner, R. "On the modeling of pedestrian motion." 
Applied Mathematical Modelling 34.2 (2010): 366-382.

\bibitem{Togashi1}
Togashi, F., Misaka, T., L\"ohner, R., and Obayashi, S. (2018). 
Using ensemble Kalman filter to determine parameters for computational crowd dynamics simulations. 
Engineering Computations, 35(7), 2612-2628.

\bibitem{kwak}
Kwak, J, Hang-Hyun, J., Luttinen, T., and Kosonen, L., 2017. "Jamming 
transitions induced by an attraction in pedestrian flow." Physical Review E 96 
(2), 022319.
{\path{https://doi.org/10.1103/PhysRevE.96.022319}}

\bibitem{johansson1}
Johansson, A., Helbing, D. and Pradyumn K. Shukla, 2007. Specification of 
the social force pedestrian model by evolutionary adjustment to video tracking 
data, Advances in complex systems 10.supp02 271-288. 
{\path{https://doi.org/10.1142/S0219525907001355}}

\bibitem{parisi2}
Parisi, D. R., Gilman, M., and Moldovan, H., 2009. "A modification of the 
social force model can reproduce experimental data of pedestrian flows in 
normal 
conditions." Physica A: Statistical Mechanics and its Applications 388 
(17), 3600-3608.
{\path{https://doi.org/10.1016/j.physa.2009.05.027}}

\bibitem{seyfried2}
Seyfried, A., Steffen B., and Lippert, T., 2006. "Basics of modelling the 
pedestrian flow." Physica A: Statistical Mechanics and its Applications 368 
(1), 232-238.
{\path{https://doi.org/10.1016/j.physa.2005.11.052}}

\bibitem{johansson}
Johansson, A., 2009. "Constant-net-time headway as a key mechanism behind 
pedestrian flow dynamics." Physical review E 80 (2), 026120. 
{\path{https://doi.org/10.1103/PhysRevE.80.026120}}

\bibitem{colombi2017}
Colombi, A., Scianna, M., and Alaia, A., 2017. "A discrete 
mathematical model for the dynamics of a crowd of gazing pedestrians with and 
without an evolving environmental awareness." Computational and Applied 
Mathematics 36 (2), 1113-1141.
{\path{https://doi.org/10.1007/s40314-016-0316-x}}

\bibitem{fruin1}
Smith, R. A., and Dickie, J. F., 1995. "Engineering for Crowd Safety.", 237-238.

\bibitem{mori1}
Mori, M., and Hiroshi T., 1987 "A new method for evaluation of level of 
service in pedestrian facilities." Transportation Research Part A: General 
21 (3), 223-234.
{\path{https://doi.org/10.1016/0191-2607(87)90016-1}}

\bibitem{polus1}
Polus, A., Schofer J. L., and Ushpiz, A., 1983. "Pedestrian flow and level 
of service." Journal of transportation engineering 109 (1), 46-56.
{\path{https://doi.org/10.1061/(ASCE)0733-947X(1983)109:1(46)}}

@@

\bibitem{plimpton}
Plimpton, S., 1995. "Fast parallel algorithms for short-range molecular 
dynamics." Journal of computational physics 117 (1), 1-19.
{\path{https://doi.org/10.1006/jcph.1995.1039}}

\bibitem{sticco}
Sticco, I. M., Cornes, F. E., Frank, G. A., and Dorso, C. O., 2017. "Beyond the 
faster-is-slower effect." Physical Review E 96 (5), 052303.
{\path{https://doi.org/10.1103/PhysRevE.96.052303}}

\bibitem{yu1}
Yu, W, and Johansson, A., 2007. "Modeling crowd turbulence by many-particle 
simulations." Physical review E 76 (4), 046105.
{\path{https://doi.org/10.1103/PhysRevE.76.046105}}

\bibitem{drury1}
Drury, J., Novelli, D., and Stott, C., 2013. "Representing crowd behavior in 
emergency planning guidance:‘Mass panic’ or collective resilience?." Resilience 
1 (1), 18-37.
{\path{https://doi.org/10.1080/21693293.2013.765740}}

\bibitem{lin}
Peng, L., Ma, J. and Lo, S. 2016. "Discrete element crowd model for 
pedestrian evacuation through an exit." Chinese Physics B 25 (3), 034501.
{\path{https://doi.org/10.1088/1674-1056/25/3/034501}}

@@

\bibitem{parisi1}
Pastor, J. M., Garcimart\'in, A., Gago, P. A., Peralta, J. P., 
Mart\'in-Gómez, C., Ferrer, L. M., Maza, D., Parisi, D. R., Pugnaloni, L. A., 
and Zuriguel, I, 2015. "Experimental proof of faster-is-slower in systems of 
frictional particles flowing through constrictions." Physical Review E 92 (6), 
062817. {\path{https://doi.org/10.1103/PhysRevE.92.062817}}

@@

\bibitem{helbing5}
Helbing, D., Moln\'ar, P., Farkas, I. J., and Bolay, K., 2001. "Self-organizing 
pedestrian movement." Environment and planning B: planning and design 
28 (3), 361-383.
{\path{https://doi.org/10.1068/b2697}}

\bibitem{feliciani1}
Feliciani, C, and Katsuhiro N., 2016. "Empirical analysis of the lane 
formation process in bidirectional pedestrian flow." Physical Review E 94 
(3), 032304.
{\path{https://doi.org/10.1103/PhysRevE.94.032304}}

@@

\bibitem{guo1}
Wei, G., Wang X., and Zheng, X., 2015. "Lane formation in pedestrian 
counterflows driven by a potential field considering following and avoidance 
behaviours." Physica A: Statistical Mechanics and its Applications 432, 87-101.
{\path{https://doi.org/10.1016/j.physa.2015.03.020}}

\bibitem{qiao1}
Jing, Q., Lishan, S., Shi, Q., Jian, R.  and Xiaoming L., 2017. 
"Reducing Bidirectional Pedestrian Conflict Based on Lane Formation Phenomenon 
in Subway Corridors." Promet-Traffic\&Transportation 29 (5), 489-502.
{\path{https://doi.org/10.7307/ptt.v29i5.2168}}

@@

\bibitem{li1}
Li, M., Zhao, Y., He, L., Chen, W. and Xu, X. 
2015. "The parameter calibration and optimization of social force model for the 
real-life 2013 Ya’an earthquake evacuation in China." Safety science 79, 
243-253.
{\path{https://doi.org/10.1016/j.ssci.2015.06.018}}

>>>>

  \bibitem{Hirai}
Hirai, K., and Tarui, K., 1975. ``A simulation of the behavior of 
a crowd in panic", Proceedings of the 1975 International
Conference on Cybernetics Society, pp. 409-411

 \bibitem[Okazaki (1979)]{Okazaki}
Okazaki, S., 1979. ``A study of pedestrian movement in 
architectural space, Part 
1: pedestrian movement by the application of magnetic model". Trans. A.I.J. 283, 
111–119.

\bibitem{Helbing1}
Helbing, D., Farkas, I., and Vicsek, T., 2000. ``Simulating dynamical 
features of escape panic." Nature 407.6803: 487-490. 
{\path{https://doi.org/10.1038/35035023}}

\bibitem{Helbing4}
Helbing, D., and Moln\'ar, P., 1995. ``Social force model for pedestrian 
dynamics." Physical review E 51 (5), 4282. 
{\path{https://doi.org/10.1103/PhysRevE.51.4282}}

\bibitem{Dorso2}
Parisi, D. R., and Dorso, C. O., 2007. ``Morphological and dynamical 
aspects of the room evacuation process." Physica A: Statistical Mechanics and 
its Applications 385 (1), 343-355. 
{\path{https://doi.org/10.1016/j.physa.2007.06.033}}

\bibitem{Dorso1}
Parisi, D. R., and Dorso, C. O., 2005. ``Microscopic dynamics of pedestrian 
evacuation." Physica A: Statistical Mechanics and its Applications 354, 
606-618. {\path{https://doi.org/10.1016/j.physa.2005.02.040}}

\bibitem{Dorso3}
Frank, G. A., and Dorso, C. O., 2011. ``Room evacuation in 
the presence of an obstacle." Physica A: Statistical Mechanics and its 
Applications 390 (11), 2135-2145. 
{\path{https://doi.org/10.1016/j.physa.2011.01.015}}

\bibitem{Dorso5}
Sticco, I. M., Frank, G. A., and Dorso, C. O., 2017. ``Room evacuation 
through two contiguous exits." Physica A: Statistical Mechanics and its 
Applications 474, 172-185. 
{\path{https://doi.org/10.1016/j.physa.2017.01.079}}

\bibitem{Cornes1}
Cornes, F. E., Frank, G. A., and Dorso, C. O., 2017. ``High pressures in room 
evacuation processes and a first approach to the dynamics around unconscious 
pedestrians." Physica A: Statistical Mechanics and its Applications 484, 
282-298. {\path{https://doi.org/10.1016/j.physa.2017.05.013}}

\bibitem{Dorso4}
Frank, G. A., and Dorso, C. O., 2015. ``Evacuation under limited 
visibility." International Journal of Modern Physics C 26.01, 1550005.
{\path{https://doi.org/10.1142/S0129183115500059}}

\bibitem{Dorso6}
Frank, G. A., and Dorso, C. O., 2016. ``Panic evacuation of single pedestrians 
and couples." International Journal of Modern Physics C 27.08, 1650091. 
{\path{https://doi.org/10.1142/S0129183116500911}}

\bibitem{koster1}
K\"oster, G., Treml, F. and G\"odel, M., 2013. ``Avoiding 
numerical pitfalls in social force models." Physical Review E 87 (6), 063305.
{\path{https://doi.org/10.1103/PhysRevE.87.063305}}

\bibitem{chraibi1}
Seyfried, A., Schadschneider, A., Wagoum, K., Ulrich, A. and Mohcine, C., 
2011. ``Force-based models of pedestrian dynamics." Networks 
\& Heterogeneous Media 6 (3), 425-442.
{\path{10.3934/nhm.2011.6.425}}

\bibitem{dietrich1}
Dietrich, F., K\"oster, G., Seitz, M. and 
von Sivers, I., 2014. ``Bridging the gap: From cellular automata to 
differential equation models for pedestrian dynamics." Journal of Computational 
Science 5 (5), 841-846.{\path{https://doi.org/10.1016/j.jocs.2014.06.005}}

\bibitem{Lakoba}
Lakoba, T. I., Kaup, D. J., and Finkelstein, N. M., 2005. ``Modifications of the 
Helbing-Molnar-Farkas-Vicsek social force model for pedestrian evolution." 
Simulation 81 (5), 339-352.
{\path{https://doi.org/10.1177/0037549705052772}}

\bibitem{Boltes}
Boltes, M., Zhang, J., Tordeux, A., Schadschneider A., Seyfried 
A., 
2018. ``Empirical Results of Pedestrian and Evacuation Dynamics". In: Meyers R. 
(eds) Encyclopedia of Complexity and Systems Science. Springer, Berlin, 
Heidelberg

\bibitem{helbing3}
Helbing, D., Johansson, A., and Al-Abideen, H. Z., 2007. ``Dynamics of crowd 
disasters: An empirical study." Physical review E 75 (4), 046109.
{\path{https://doi.org/10.1103/PhysRevE.75.046109}}

@@

\bibitem{seyfried}
Seyfried, A., Boltes, M., K\"ahler, J., Klingsch, W., Portz, A., Rupprecht, 
T., Schadschneider, A., Steffen, B. and Winkens, A., 2010. ``Enhanced empirical 
data for the fundamental diagram and the flow through bottlenecks." Pedestrian 
and Evacuation Dynamics 2008. Springer, Berlin, Heidelberg. 145-156.
{\path{https://doi.org/10.1007/978-3-642-04504-2\_11}}

\bibitem{lohner1}
L\"ohner, R., Muhamad, B., Dambalmath, P., and Haug, E., 2018. 
``Fundamental diagrams for specific very high density crowds." Collective 
Dynamics 2, 1-15.
{\path{http://dx.doi.org/10.17815/CD.2017.13}}

\bibitem{Dridi1}
Dridi, M. (2015) ``Pedestrian Flow Simulation Validation and
Verification Techniques". Current Urban Studies, 3, 119-134.
doi: 10.4236/cus.2015.32011.

\bibitem{Dridi2}
Dridi, M. (2015) ``Simulation of High Density Pedestrian Flow:
A Microscopic Model". Open Journal of Modelling and Simulation,
3, 81-95. doi: 10.4236/ojmsi.2015.33009.

\bibitem{Baqui1}
Baqui, M., and L\"ohner, R. ``Real-time crowd safety
and comfort management from CCTV images." Real-Time Image and Video Processing 2017.
Vol. 10223. International Society for Optics and Photonics, 2017.

\bibitem{lohner2}
L\"ohner, R. ``On the modeling of pedestrian motion." 
Applied Mathematical Modelling 34.2 (2010): 366-382.

\bibitem{Togashi1}
Togashi, F., Misaka, T., L\"ohner, R., and Obayashi, S. (2018). 
``Using ensemble Kalman filter to determine parameters for computational crowd dynamics simulations. 
Engineering Computations", 35(7), 2612-2628.

\bibitem{kwak}
Kwak, J, Hang-Hyun, J., Luttinen, T., and Kosonen, L., 2017. ``Jamming 
transitions induced by an attraction in pedestrian flow." Physical Review E 96 
(2), 022319.
{\path{https://doi.org/10.1103/PhysRevE.96.022319}}

\bibitem{johansson1}
Johansson, A., Helbing, D. and Pradyumn K. Shukla, 2007. ``Specification of 
the social force pedestrian model by evolutionary adjustment to video tracking 
data", Advances in complex systems 10.supp02 271-288. 
{\path{https://doi.org/10.1142/S0219525907001355}}

\bibitem{parisi2}
Parisi, D. R., Gilman, M., and Moldovan, H., 2009. ``A modification of the 
social force model can reproduce experimental data of pedestrian flows in 
normal 
conditions." Physica A: Statistical Mechanics and its Applications 388 
(17), 3600-3608.
{\path{https://doi.org/10.1016/j.physa.2009.05.027}}

\bibitem{seyfried2}
Seyfried, A., Steffen B., and Lippert, T., 2006. ``Basics of modelling the 
pedestrian flow." Physica A: Statistical Mechanics and its Applications 368 
(1), 232-238.
{\path{https://doi.org/10.1016/j.physa.2005.11.052}}

\bibitem{johansson}
Johansson, A., 2009. ``Constant-net-time headway as a key mechanism behind 
pedestrian flow dynamics." Physical review E 80 (2), 026120. 
{\path{https://doi.org/10.1103/PhysRevE.80.026120}}

\bibitem{colombi2017}
Colombi, A., Scianna, M., and Alaia, A., 2017. ``A discrete 
mathematical model for the dynamics of a crowd of gazing pedestrians with and 
without an evolving environmental awareness." Computational and Applied 
Mathematics 36 (2), 1113-1141.
{\path{https://doi.org/10.1007/s40314-016-0316-x}}

\bibitem{fruin1}
Smith, R. A., and Dickie, J. F., 1995. ``Engineering for Crowd Safety.", 237-238.

\bibitem{mori1}
Mori, M., and Hiroshi T., 1987 ``A new method for evaluation of level of 
service in pedestrian facilities." Transportation Research Part A: General 
21 (3), 223-234.
{\path{https://doi.org/10.1016/0191-2607(87)90016-1}}

\bibitem{polus1}
Polus, A., Schofer J. L., and Ushpiz, A., 1983. ``Pedestrian flow and level 
of service." Journal of transportation engineering 109 (1), 46-56.
{\path{https://doi.org/10.1061/(ASCE)0733-947X(1983)109:1(46)}}

@@

\bibitem{plimpton}
Plimpton, S., 1995. ``Fast parallel algorithms for short-range molecular 
dynamics." Journal of computational physics 117 (1), 1-19.
{\path{https://doi.org/10.1006/jcph.1995.1039}}

\bibitem{sticco}
Sticco, I. M., Cornes, F. E., Frank, G. A., and Dorso, C. O., 2017. ``Beyond the 
faster-is-slower effect." Physical Review E 96 (5), 052303.
{\path{https://doi.org/10.1103/PhysRevE.96.052303}}

\bibitem{yu1}
Yu, W, and Johansson, A., 2007. ``Modeling crowd turbulence by many-particle 
simulations." Physical review E 76 (4), 046105.
{\path{https://doi.org/10.1103/PhysRevE.76.046105}}

\bibitem{drury1}
Drury, J., Novelli, D., and Stott, C., 2013. ``Representing crowd behavior in 
emergency planning guidance:‘Mass panic’ or collective resilience?." Resilience 
1 (1), 18-37.
{\path{https://doi.org/10.1080/21693293.2013.765740}}

\bibitem{lin}
Peng, L., Ma, J. and Lo, S. 2016. ``Discrete element crowd model for 
pedestrian evacuation through an exit." Chinese Physics B 25 (3), 034501.
{\path{https://doi.org/10.1088/1674-1056/25/3/034501}}

@@

\bibitem{parisi1}
Pastor, J. M., Garcimart\'in, A., Gago, P. A., Peralta, J. P., 
Mart\'in-Gómez, C., Ferrer, L. M., Maza, D., Parisi, D. R., Pugnaloni, L. A., 
and Zuriguel, I, 2015. ``Experimental proof of faster-is-slower in systems of 
frictional particles flowing through constrictions." Physical Review E 92 (6), 
062817. {\path{https://doi.org/10.1103/PhysRevE.92.062817}}

@@

\bibitem{helbing5}
Helbing, D., Moln\'ar, P., Farkas, I. J., and Bolay, K., 2001. ``Self-organizing 
pedestrian movement." Environment and planning B: planning and design 
28 (3), 361-383.
{\path{https://doi.org/10.1068/b2697}}

\bibitem{feliciani1}
Feliciani, C, and Katsuhiro N., 2016. ``Empirical analysis of the lane 
formation process in bidirectional pedestrian flow." Physical Review E 94 
(3), 032304.
{\path{https://doi.org/10.1103/PhysRevE.94.032304}}

@@

\bibitem{guo1}
Wei, G., Wang X., and Zheng, X., 2015. ``Lane formation in pedestrian 
counterflows driven by a potential field considering following and avoidance 
behaviours." Physica A: Statistical Mechanics and its Applications 432, 87-101.
{\path{https://doi.org/10.1016/j.physa.2015.03.020}}

\bibitem{qiao1}
Jing, Q., Lishan, S., Shi, Q., Jian, R.  and Xiaoming L., 2017. 
``Reducing Bidirectional Pedestrian Conflict Based on Lane Formation Phenomenon 
in Subway Corridors." Promet-Traffic\&Transportation 29 (5), 489-502.
{\path{https://doi.org/10.7307/ptt.v29i5.2168}}

@@

\bibitem{li1}
Li, M., Zhao, Y., He, L., Chen, W. and Xu, X. 
2015. ``The parameter calibration and optimization of social force model for the 
real-life 2013 Ya’an earthquake evacuation in China." Safety science 79, 
243-253.
{\path{https://doi.org/10.1016/j.ssci.2015.06.018}}
